Interpolation of Sparse High-Dimensional Data\thanks {This work was supported by the National Science Foundation Grant CNS-1565314.}

### 2019-03-30 Paper_[2019-02]_Numerical_Algorithms/paper.tex
Final update before submission.

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l}
    Algorithm & \multicolumn{2}{c|}{Avg. \% Best} & \multicolumn{2}{c|}{\multilinecell{Avg. Fit or \\ Prep. Time (s)}} & \multicolumn{2}{c}{Avg. App. Time (s)}\\
    \hline
    MARS & \quad\quad$4$&$6$ & \,\quad$20$&$0$ & \quad\quad$0$&$001$\\
    SVR & $\mathit{21}$&$\mathit{1}$ & $\mathit{0}$&$\mathit{5}$ & $\mathbf{0}$&$\mathbf{0001}$\\
    MLP & $\mathbf{42}$&$\mathbf{1}$ & $200$&$0$ & $0$&$001$\\
    Delaunay & $6$&$0$ & $1$&$0$ & $1$&$0$\\
    ShepMod & $18$&$4$ & $0$&$7$ & $\mathbf{0}$&$\mathbf{0001}$\\
    LSHEP & $8$&$4$ & $2$&$0$ & $\mathbf{0}$&$\mathbf{0001}$\\
    Voronoi & $0$&$5$ & $\mathbf{0}$&$\mathbf{1}$ & $0$&$04$\\
    BoxSpline & $0$&$2$ & $0$&$8$ & $\mathit{0}$&$\mathit{0005}$\\
  \end{tabular}
  \caption{This average of Appendix Tables
    \ref{table:best-forest-fire}, \ref{table:best-parkinsons},
    \ref{table:best-weather}, and \ref{table:best-credit-card}
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time to fit/prepare, and the
    average time required to approximate one point. The times have
    been rounded to one significant digit, as reasonably large
    fluctuations may be observed due to implementation hardware.
    Interpolants provide the lowest error approximation for nearly one
    third of all data, while regressors occupy the other two
    thirds. This result is obtained without any customized tuning or
    preprocessing to maximize the performance of any given
    algorithm. In practice, tuning and preprocessing may have large
    effects on approximation performance.}
  \label{table:avg-performance}
\end{table}

@@

The major contributions of this work are: 1) new uniform theoretical
error bounds for piecewise linear interpolation in arbitrary dimension
(Section \ref{sec:theory}); 2) an empirical evaluation across
real-world problems (Section \ref{sec:data}) that demonstrates
interpolants produce competitively accurate models of multivariate
phenomenon when compared with common regressors for sparse, moderately
high dimensional problems; and 3) a demonstration that some
interpolants generalize to interpolation in function spaces,
preserving monotonicity (with CDFs, e.g.), neither of which common
regressors can do.

The various interpolants discussed in this paper have been
demonstrated to effectively approximate multivariate phenomena up to
$30$ dimensions. The underlying constructions are theoretically
straightforward, interpretable, and yield reasonably accurate
predictions. Most of the interpolants' computational complexities make
them particularly suitable for applications in even higher
dimension. The major benefits of interpolation are seen when only a
small number of approximations ($\leq 1000$) are made from data and
when there are relatively few data points for the dimension (for
empirical results presented, $\log_d n \leq 5$).

@@

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad$\mathit{7}$&$\mathit{7}$ &  & \quad\quad$29$&$1$ & \quad$0$&$00137$ & \quad\quad\quad$0$&$0686$\\
    SVR & $\mathbf{80}$&$\mathbf{2}$ &  & $\mathit{0}$&$\mathit{00584}$ & $\mathit{0}$&$\mathit{0000620}$ & $\mathit{0}$&$\mathit{00310}$\\
    MLP & $0$&$0$ &  & $32$&$8$ & $0$&$000871$ & $0$&$0436$\\
    Delaunay & $3$&$5$ &  & $0$&$0151$ & $0$&$0234$ & $1$&$18$\\
    ShepMod & $3$&$7$ &  & $0$&$00634$ & $0$&$0000644$ & $0$&$00322$\\
    LSHEP & $5$&$1$ &  & $0$&$0275$ & $\mathbf{0}$&$\mathbf{0000463}$ & $\mathbf{0}$&$\mathbf{00231}$\\
    Voronoi & $0$&$0$ &  & $\mathbf{0}$&$\mathbf{000182}$ & $0$&$000396$ & $0$&$0198$\\
    BoxSpline & $0$&$4$ &  & $0$&$00724$ & $0$&$0000978$ & $0$&$00489$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating forest fire data in Table
    \ref{table:error-forest-fire}. On the right columns are median fit
    time of 454 points, median time for one approximation, and median
    time approximating 50 points.}
  \label{table:best-forest-fire}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad\quad$37$&$9$ & \quad\,\,$0$&$00253$ & \quad\quad\quad\,\,$1$&$48$\\
    SVR & $0$&$1$ &  & $\mathit{0}$&$\mathit{859}$ & $\mathit{0}$&$\mathit{000181}$ & $\mathit{0}$&$\mathit{106}$\\
    MLP & $\mathit{32}$&$\mathit{0}$ &  & $348$&$0$ & $0$&$00111$ & $0$&$653$\\
    Delaunay & $0$&$0$ &  & $2$&$47$ & $1$&$22$ & $720$&$0$\\
    ShepMod & $\mathbf{66}$&$\mathbf{4}$ &  & $1$&$13$ & $0$&$000182$ & $0$&$107$\\
    LSHEP & $0$&$0$ &  & $2$&$39$ & $\mathbf{0}$&$\mathbf{000144}$ & $\mathbf{0}$&$\mathbf{0845}$\\
    Voronoi & $1$&$6$ &  & $\mathbf{0}$&$\mathbf{298}$ & $0$&$0274$ & $16$&$1$\\
    BoxSpline & $0$&$0$ &  & $1$&$26$ & $0$&$000643$ & $0$&$377$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating Parkinson's data in Table
    \ref{table:error-parkinsons}. On the right columns are median fit
    time of 5288 points, median time for one approximation, and median
    time approximating 587 points.}
  \label{table:best-parkinsons}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \,\,\,\,$10$&$7$ &  & \quad\quad\quad$0$&$151$ & \quad$0$&$000117$ & \quad\quad\quad\,\,$0$&$0304$\\
    SVR & $4$&$1$ &  & $\mathit{0}$&$\mathit{133}$ & $\mathbf{0}$&$\mathbf{0000947}$ & $\mathbf{0}$&$\mathbf{0246}$\\
    MLP & $\mathbf{56}$&$\mathbf{8}$ &  & $169$&$0$ & $0$&$00137$ & $0$&$356$\\
    Delaunay & $0$&$1$ &  & $0$&$664$ & $0$&$886$ & $230$&$0$\\
    ShepMod & $3$&$5$ &  & $0$&$265$ & $0$&$000128$ & $0$&$0333$\\
    LSHEP & $\mathit{28}$&$\mathit{4}$ &  & $0$&$874$ & $\mathit{0}$&$\mathit{0000975}$ & $\mathit{0}$&$\mathit{0254}$\\
    Voronoi & $0$&$2$ &  & $\mathbf{0}$&$\mathbf{012}$ & $0$&$0270$ & $7$&$01$\\
    BoxSpline & $0$&$3$ &  & $0$&$330$ & $0$&$000406$ & $0$&$106$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{Left table shows how often each algorithm had the lowest
    absolute error approximating Sydney rainfall data in Table
    \ref{table:error-weather}. On the right columns are median fit
    time of 2349 points, median time for one approximation, and median
    time approximating 260 points.}
  \label{table:best-weather}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad\quad$22$&$0$ & \quad$0$&$00148$ & \quad\quad\quad\,\,$0$&$820$\\
    SVR & $0$&$0$ &  & $\mathit{1}$&$\mathit{01}$ & $\mathit{0}$&$\mathit{000210}$ & $\mathit{0}$&$\mathit{117}$\\
    MLP & $\mathbf{79}$&$\mathbf{5}$ &  & $290$&$0$ & $0$&$000714$ & $0$&$397$\\
    Delaunay & $\mathit{20}$&$\mathit{5}$ &  & $3$&$12$ & $3$&$71$ & $2070$&$0$\\
    ShepMod & $0$&$1$ &  & $1$&$45$ & $0$&$000220$ & $0$&$122$\\
    LSHEP & $0$&$0$ &  & $3$&$47$ & $\mathbf{0}$&$\mathbf{000176}$ & $\mathbf{0}$&$\mathbf{0981}$\\
    Voronoi & $0$&$0$ &  & $\mathbf{0}$&$\mathbf{197}$ & $0$&$0950$ & $52$&$8$\\
    BoxSpline & $0$&$0$ &  & $1$&$66$ & $0$&$000956$ & $0$&$532$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating credit card transaction data
    in Table \ref{table:error-credit-card}. On the right columns are
    median fit time of 5006 points, median time for one approximation,
    and median time approximating 556 points.}
  \label{table:best-credit-card}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    Delaunay & \,\,$\mathbf{62}$&$\mathbf{0}$ &  & \quad\quad\quad$0$&$344$ & \quad$0$&$00984$ & \quad\quad\,\,$2$&$71$\\
    ShepMod & $0$&$0$ &  & $\mathbf{0}$&$\mathbf{0884}$ & $\mathbf{0}$&$\mathbf{000145}$ & $\mathbf{0}$&$\mathbf{0436}$\\
    Voronoi & $\mathit{38}$&$\mathit{0}$ &  & $1$&$0$ & $0$&$00253$ & $0$&$762$\\
    BoxSpline & $0$&$0$ &  & $0$&$0972$ & $\mathit{0}$&$\mathit{000210}$ & $\mathit{0}$&$\mathit{0633}$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest KS statistic on the I/O throughput distribution data in
    Table \ref{table:error-throughput}. On the right columns are
    median fit time of 2715 points, median time for one approximation,
    and median time approximating 301 points.}
  \label{table:best-throughput}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{tabular}{c|r@{.}l|r@{.}l|r@{.}l}
    Algorithm & \multicolumn{2}{c|}{Avg. \% Best} & \multicolumn{2}{c|}{\multilinecell{Avg. Fit or \\ Prep. Time (s)}} & \multicolumn{2}{c}{Avg. App. Time (s)}\\
    \hline
    MARS & \quad\quad$4$&$6$ & \,\quad$20$&$0$ & \quad\quad$0$&$001$\\
    SVR & $\mathit{21}$&$\mathit{1}$ & $\mathbf{0}$&$\mathbf{5}$ & $\mathbf{0}$&$\mathbf{0001}$\\
    MLP & $\mathbf{42}$&$\mathbf{1}$ & $200$&$0$ & $0$&$001$\\
    Delaunay & $6$&$0$ & $1$&$0$ & $1$&$0$\\
    ShepMod & $18$&$4$ & $\mathit{0}$&$\mathit{7}$ & $\mathbf{0}$&$\mathbf{0001}$\\
    LSHEP & $8$&$4$ & $2$&$0$ & $\mathbf{0}$&$\mathbf{0001}$\\
    Voronoi & $0$&$5$ & $1$&$0$ & $0$&$04$\\
    BoxSpline & $0$&$2$ & $0$&$8$ & $\mathit{0}$&$\mathit{0005}$\\
  \end{tabular}
  \caption{This average of Appendix Tables
    \ref{table:best-forest-fire}, \ref{table:best-parkinsons},
    \ref{table:best-weather}, and \ref{table:best-credit-card}
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time to fit/prepare, and the
    average time required to approximate one point. The times have
    been rounded to one significant digit, as reasonably large
    fluctuations may be observed due to implementation hardware.
    Interpolants provide the lowest error approximation for nearly one
    third of all data, while regressors occupy the other two
    thirds. This result is obtained without any customized tuning or
    preprocessing to maximize the performance of any given
    algorithm. In practice, tuning and preprocessing may have large
    effects on approximation performance.}
  \label{table:avg-performance}
\end{table}

@@

The major contributions of this work are: 1) new uniform theoretical
error bounds for piecewise linear interpolation in arbitrary dimension
(Section \ref{sec:theory}); 2) an empirical evaluation across
real-world problems that demonstrates interpolants produce
competitively accurate models of multivariate phenomenon when compared
with common regressors for sparse, moderately high dimensional
problems (Section \ref{sec:data}); and 3) a demonstration that some
interpolants generalize to interpolation in function spaces (Section
\ref{sec:error}), preserving monotonicity (with CDFs, e.g.), neither
of which common regressors can do.

The various interpolants discussed in this paper have been
demonstrated to effectively approximate multivariate phenomena up to
$30$ dimensions. The underlying constructions are theoretically
straightforward, interpretable, and yield reasonably accurate
predictions. Most of the interpolants' computational complexities make
them particularly suitable for applications in even higher
dimension. The major benefits of interpolation are seen when only a
small number of approximations ($\leq 1000$) are made from data and
when there are relatively few data points for the dimension (for
empirical results presented, $\log_d n \leq 5$). These findings
encourage broader application of interpolants to multivariate
approximation in science

@@

The tables that follow show the precise experimental results for all
data sets presented in Section \ref{sec:data}. The tests were all run
serially on an otherwise idle machine with a CentOS 6.10 operating
system and an Intel i7-3770 CPU operating at 3.4 GHz. The detailed
performance results in the tables that follow are very much dependent
on the problem and the algorithm implementation (e.g., some codes are
TOMS software, some industry distributions, and others are from
conference paper venues). Different typeface is used to show best
performers, however not much significance should be attached to
ranking algorithms based on small time (millisecond) differences. The
results serve as a demonstration of conceptual validity.

@@

\begin{table}[H]
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad$\mathit{7}$&$\mathit{7}$ &  & \quad\quad$29$&$1$ & \quad$0$&$00137$ & \quad\quad\quad$0$&$0686$\\
    SVR & $\mathbf{80}$&$\mathbf{2}$ &  & $\mathbf{0}$&$\mathbf{00584}$ & $\mathit{0}$&$\mathit{0000620}$ & $\mathit{0}$&$\mathit{00310}$\\
    MLP & $0$&$0$ &  & $32$&$8$ & $0$&$000871$ & $0$&$0436$\\
    Delaunay & $3$&$5$ &  & $0$&$0151$ & $0$&$0234$ & $1$&$18$\\
    ShepMod & $3$&$7$ &  & $\mathit{0}$&$\mathit{00634}$ & $0$&$0000644$ & $0$&$00322$\\
    LSHEP & $5$&$1$ &  & $0$&$0275$ & $\mathbf{0}$&$\mathbf{0000463}$ & $\mathbf{0}$&$\mathbf{00231}$\\
    Voronoi & $0$&$0$ &  & $0$&$0152$ & $0$&$000396$ & $0$&$0198$\\
    BoxSpline & $0$&$4$ &  & $0$&$00724$ & $0$&$0000978$ & $0$&$00489$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating forest fire data in Table
    \ref{table:error-forest-fire}. On the right columns are median fit
    time of 454 points, median time for one approximation, and median
    time approximating 50 points.}
  \label{table:best-forest-fire}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad\quad$37$&$9$ & \quad\,\,$0$&$00253$ & \quad\quad\quad\,\,$1$&$48$\\
    SVR & $0$&$1$ &  & $\mathbf{0}$&$\mathbf{859}$ & $\mathit{0}$&$\mathit{000181}$ & $\mathit{0}$&$\mathit{106}$\\
    MLP & $\mathit{32}$&$\mathit{0}$ &  & $348$&$0$ & $0$&$00111$ & $0$&$653$\\
    Delaunay & $0$&$0$ &  & $2$&$47$ & $1$&$22$ & $720$&$0$\\
    ShepMod & $\mathbf{66}$&$\mathbf{4}$ &  & $\mathit{1}$&$\mathit{13}$ & $0$&$000182$ & $0$&$107$\\
    LSHEP & $0$&$0$ &  & $2$&$39$ & $\mathbf{0}$&$\mathbf{000144}$ & $\mathbf{0}$&$\mathbf{0845}$\\
    Voronoi & $1$&$6$ &  & $2$&$77$ & $0$&$0274$ & $16$&$1$\\
    BoxSpline & $0$&$0$ &  & $1$&$26$ & $0$&$000643$ & $0$&$377$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating Parkinson's data in Table
    \ref{table:error-parkinsons}. On the right columns are median fit
    time of 5288 points, median time for one approximation, and median
    time approximating 587 points.}
  \label{table:best-parkinsons}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \,\,\,\,$10$&$7$ &  & \quad\quad\quad$\mathit{0}$&$\mathit{151}$ & \quad$0$&$000117$ & \quad\quad\quad\,\,$0$&$0304$\\
    SVR & $4$&$1$ &  & $\mathbf{0}$&$\mathbf{133}$ & $\mathbf{0}$&$\mathbf{0000947}$ & $\mathbf{0}$&$\mathbf{0246}$\\
    MLP & $\mathbf{56}$&$\mathbf{8}$ &  & $169$&$0$ & $0$&$00137$ & $0$&$356$\\
    Delaunay & $0$&$1$ &  & $0$&$664$ & $0$&$886$ & $230$&$0$\\
    ShepMod & $3$&$5$ &  & $0$&$265$ & $0$&$000128$ & $0$&$0333$\\
    LSHEP & $\mathit{28}$&$\mathit{4}$ &  & $0$&$874$ & $\mathit{0}$&$\mathit{0000975}$ & $\mathit{0}$&$\mathit{0254}$\\
    Voronoi & $0$&$2$ &  & $0$&$675$ & $0$&$0270$ & $7$&$01$\\
    BoxSpline & $0$&$3$ &  & $0$&$330$ & $0$&$000406$ & $0$&$106$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{Left table shows how often each algorithm had the lowest
    absolute error approximating Sydney rainfall data in Table
    \ref{table:error-weather}. On the right columns are median fit
    time of 2349 points, median time for one approximation, and median
    time approximating 260 points.}
  \label{table:best-weather}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    MARS & \quad\,$0$&$0$ &  & \quad\quad\quad$22$&$0$ & \quad$0$&$00148$ & \quad\quad\quad\,\,$0$&$820$\\
    SVR & $0$&$0$ &  & $\mathbf{1}$&$\mathbf{01}$ & $\mathit{0}$&$\mathit{000210}$ & $\mathit{0}$&$\mathit{117}$\\
    MLP & $\mathbf{79}$&$\mathbf{5}$ &  & $290$&$0$ & $0$&$000714$ & $0$&$397$\\
    Delaunay & $\mathit{20}$&$\mathit{5}$ &  & $3$&$12$ & $3$&$71$ & $2070$&$0$\\
    ShepMod & $0$&$1$ &  & $\mathit{1}$&$\mathit{4}5$ & $0$&$000220$ & $0$&$122$\\
    LSHEP & $0$&$0$ &  & $3$&$47$ & $\mathbf{0}$&$\mathbf{000176}$ & $\mathbf{0}$&$\mathbf{0981}$\\
    Voronoi & $0$&$0$ &  & $3$&$32$ & $0$&$0950$ & $52$&$8$\\
    BoxSpline & $0$&$0$ &  & $1$&$66$ & $0$&$000956$ & $0$&$532$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest absolute error approximating credit card transaction data
    in Table \ref{table:error-credit-card}. On the right columns are
    median fit time of 5006 points, median time for one approximation,
    and median time approximating 556 points.}
  \label{table:best-credit-card}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|c|r@{.}l| c |r@{.}l|r@{.}l|r@{.}l|}
    \cline{1-3}\cline{5-10}
    Algorithm & \multicolumn{2}{c|}{\% Best} &  & \multicolumn{2}{c|}{Fit/Prep. Time (s)} & \multicolumn{2}{c|}{App. Time (s)} & \multicolumn{2}{c|}{Total App. Time (s)}\\
    \cline{1-3}\cline{5-10}
    Delaunay & \,\,$\mathbf{62}$&$\mathbf{0}$ &  & \quad\quad\quad$0$&$344$ & \quad$0$&$00984$ & \quad\quad\,\,$2$&$71$\\
    ShepMod & $0$&$0$ &  & $\mathbf{0}$&$\mathbf{0884}$ & $\mathbf{0}$&$\mathbf{000145}$ & $\mathbf{0}$&$\mathbf{0436}$\\
    Voronoi & $\mathit{38}$&$\mathit{0}$ &  & $0$&$360$ & $0$&$00253$ & $0$&$762$\\
    BoxSpline & $0$&$0$ &  & $\mathit{0}$&$\mathit{0972}$ & $\mathit{0}$&$\mathit{000210}$ & $\mathit{0}$&$\mathit{0633}$\\
    \cline{1-3}\cline{5-10}
  \end{tabular}
  \caption{The left above shows how often each algorithm had the
    lowest KS statistic on the I/O throughput distribution data in
    Table \ref{table:error-throughput}. On the right columns are
    median fit time of 2715 points, median time for one approximation,
    and median time approximating 301 points.}
  \label{table:best-throughput}
\end{table}
